A reproducible journal article with RMarkdown&#58; A  building science template with examples for beginners based on the Elsevier journal format

### 2019-02-27 Paper/Manuscript.Rmd
Add note + spellcheck example

```{r echo=TRUE, message=FALSE, warning=FALSE}
# Example of generating BibTex file for the packages listed below
# Note the output location is specified 
pkgs <- c("here", "knitr", "ggpmisc", "gt", "grateful", "base", "rticles", "bookdown", 
          "rmarkdown", "tidyverse")
cites <- grateful::get_citations(pkgs, filename = "pkg-refs.bib",
                    out.dir =  here("/Paper/SupplementaryMaterial/Software_citations") )
```

>>>>

```{r echo=TRUE, message=FALSE, warning=FALSE}
# Example of generating BibTex file for the packages listed below
# Note the output location is specified 
pkgs <- c("here", "knitr", "ggpmisc", "gt", "grateful", "base", "rticles", "bookdown", 
          "rmarkdown")
cites <- grateful::get_citations(pkgs, filename = "pkg-refs.bib",
                    out.dir =  here("/Paper/SupplementaryMaterial/Software_citations") )
```
